Universal Anonymous Signatures

### 2022-10-05 prism-backend/research/gsac/app-related-proofs.tex
Spellchecked abstract and intro.
Typos and notation fixed. Some important updates pending...

\begin{proof}
  Assume an adversary \adv~ against anonymity in \CUASGS. This directly leads
  to an adverary \advB against anonymity of the $(\fissue^1,\feval^0,
  \finsp^{\upk})-\CUASGen$ instance.

  Concretely, observe that calls to \adv's $Ch,Open,SndToU,WReg,USK,CrptU$
  oracles can be directly simulated by calls to \advB's oracles $\CHALb,
  \OPEN,\HUGEN,\WREG,\CUGEN,\UCORR$ oracles. Thus, if \adv~guesses its bit $b$
  with non-negligible probability, this directly leads to a non-negligible
  probability of guessing \advB's challenge bit.
  \qed
\end{proof}

@@

  \advB's simulation of \adv's environment is as in the proof for anonymity
  of \CUASGS. \advB simply outputs whatever \adv~outputs in line 2 of its
  traceability game. Note that, whenever \CUASGS accepts a signature, so does
  \CUASGen. Concretely,
  assume that \adv~wins the traceability game in \figref{fig:model-gs} with
  $\upk \notin \HU \cup \CU$ at line 5. This implies that, in line 10 of the
  \UAS signature unforgeability game (\figref{fig:exp-uas-unfor}) $\OWNR[\lbrace
  \cid_i\rbrace_{i\in[n]}]$ returns an \uid which is not in either \HU or \CU.
  Similarly, if \adv~wins the traceability game with condition $\Judge(\dots)=0$
  at line 5, then \advB wins its signature unforgeability game with the
  corresponding check at line 11 in \figref{fig:exp-uas-unfor}.
  %
  \qed
\end{proof}

@@

\begin{proof}
  Assume $\adv$ is an adversary against ring signature anonymity for \CUASRing.
  Then, we build \advB against anonymity of \CUASGen. Concretely, \advB first
  generates $n$ key pairs for \adv simulating $KeyGen$ in \adv's game. Since
  $KeyGen$ simply uses algorithms of $\CUASGen^{hide-iss}$, \advB can do this
  directly via its own \HUGEN, \ISET, and \OGEN oracles, specifying
  $\fissue^{\sring}$ as issuance function, and $\finsp^0$ as opening function.
  Then, \advB invokes $\adv$ passing the $n$ produced public keys, and
  answers $\adv$'s $SIGN(i,R,\msg)$ queries as follows. If user $i$ has not yet
  produced a credential for ring $R$, where $\pk_i \in R$, \advB makes a call to
  its \OBTAIN oracle, using $R$ as attribute set. If such a credential was already
  produced, \advB simply reuses it. Then, \advB uses the corresponding user and
  credential identifiers as parameters to a query to its own \SIGN oracle
  (specifying $\feval^{\attrs}$ as signature evaluation function). Eventually,
  $\adv$ outputs two user indexes, a ring $R$, and message \msg. If the checks
  at lines 3-4 of \figref{fig:model-rs} pass, \advB generates the challenge
  signature by calling its own \CHALb oracle, and passes the result to $\adv$.
  Finally, \advB outputs whatever $\adv$ outputs.
  %
  The simulation of \adv's anonymity game is perfect, and \advB wins its game
  whenever \adv does.
  \qed
\end{proof}

@@

\begin{proof}
  Assume $\adv$ against unforgeability of \CUASRing wins the game. We build
  \advB winning the non-frameability game of \CUASGen with the same probability.
  %
  \advB prepares the environment as the adversary \advB against anonymity,
  and answers \adv's queries to the $SIGN$ oracle also as in the anonymity
  proof. To answer \adv's queries to its $CORR$ oracle, \advB leverages the
  \ICORR oracle in the non-frameability game for \UAS. Finally, \advB outputs
  whatever $\adv$ outputs.

  Note that, if $\adv$ wins its game, it means that the public keys of the
  issuers in $R$ all belong to uncorrupted users. Since the signature is
  accepted by $Verify$ at line 3 of the ring signature unforgeability game,
  it is also accepted by \Verify in the \UAS non-frameability game. But,
  moreover, given the construction of $Verify$ in \CUASRing, there is some
  honest \usk within $R$ that produced the signature, so $\OWNR[\scid] \in \HU$
  in \advB's non-frameability game. Also, since $\adv$ never queried its $SIGN$
  oracle, then by construction there cannot exist a matching entry in \advB's
  $\SIG[\uid]$ table. Thus, \advB wins the non-frameability game whenever
  $\adv$ wins its unforgeability game. Since \CUASGen is non-frameable, then
  this probability must be negligible.
  %
  \qed
\end{proof}

@@

We prove that \CUASAC is an anonymous and unforgeable anonymous credential
scheme, according to \cite{fhs19}, if the underlying \CUASGen construction
is anonymous and unforgeable. Note that AC schemes modelled as in \cite{fhs19}
do not have issuance anonymity, as the user public key is passed to the issuer.
Note that, for ease of reference to the games in \secref{sec:formal-uas}, we
reduce to security of \CUASGen rather than to $\CUASGen^{int}$. The
``translation'' between \CUASGen and $\CUASGen^{int}$ is trivial, though.

\begin{theorem}[Anonymity of \CUASAC]
  \label{thm:anon-cuasac}
  If the base \CUASGen construction is anonymous according to
  \defref{def:sign-anonymity-uas}, then \CUASAC is an anonymous AC scheme
  according to \cite{fhs19}.
\end{theorem}

@@

  To simulate oracle calls by \adv, \advB simply redirects to its corresponding
  oracle, i.e.: for calls to $HU,CU,Obtain,Show,LoR$, \advB redirects to
  \HUGEN,\CUGEN,\OBTAIN,\SIGN,\CHALb, respectively. Note that translating
  the inputs from the former into inputs for the latter is trivial.
  Obviously, if \adv~wins in its anonymity game, then so does \advB with the
  same probability.
  % 
  \qed
\end{proof}

>>>>

\begin{proof}
  Assume an adversary \adv~ against anonymity in \CUASGS. This directly leads
  to an adversary \advB against anonymity of the $(\fissue^1,\feval^0,
  \finsp^{\upk})-\CUASGen$ instance.

  Concretely, observe that calls to \adv's \oracle{Ch}, \oracle{Open},
  \oracle{SndToU}, \oracle{WReg}, \oracle{USK}, \oracle{CrptU}
  oracles can be directly simulated by calls to \advB's oracles $\CHALb,
  \OPEN,\HUGEN,\OBTAIN,\WREG,\CUGEN,\UCORR$ oracles. Thus, if \adv~guesses its
  bit $b$ with non-negligible probability, this directly leads to a
  non-negligible probability of guessing \advB's challenge bit.
  \qed
\end{proof}

@@

  \advB's simulation of \adv's environment is as in the proof for anonymity
  of \CUASGS (leveraging the \OBTISS and \ISSUE oracles, instead of \OBTAIN).
  \advB simply outputs whatever \adv~outputs in line 2 of its
  traceability game. Note that, whenever \CUASGS accepts a signature, so does
  \CUASGen. Concretely,
  assume that \adv~wins the traceability game in \figref{fig:model-gs} with
  $\upk \notin \HU \cup \CU$ at line 5. This implies that, in line 10 of the
  \UAS signature unforgeability game (\figref{fig:exp-uas-unfor}) $\OWNR[\lbrace
  \cid_i\rbrace_{i\in[n]}]$ returns an \uid which is not in either \HU or \CU.
  Similarly, if \adv~wins the traceability game with condition $\Judge(\dots)=0$
  at line 5, then \advB wins its signature unforgeability game with the
  corresponding check at line 11 in \figref{fig:exp-uas-unfor}.
  %
  \qed
\end{proof}

@@

\begin{proof}
  Assume \adv~is an adversary against anonymity for \CUASRing.
  Then, we build \advB against anonymity of \CUASGen. Concretely, \advB first
  generates $n$ key pairs for \adv~ simulating $KeyGen$ in \adv's game. Since
  $KeyGen$ simply uses algorithms of $\CUASGen^{hide-iss}$, \advB can do this
  directly via its own \HUGEN, \ISET, and \OGEN oracles, specifying
  $\fissue^{\sring}$ as issuance function, and $\finsp^0$ as opening function.
  Then, \advB invokes $\adv$ passing the $n$ produced public keys, and answers
  \adv's \oracle{SIGN}(i,R,\msg) queries as follows. If user $i$ has not yet
  produced a credential for ring $R$, where $\pk_i \in R$, \advB makes a call to
  its \OBTAIN oracle, using $R$ as attribute set. If such a credential was already
  produced, \advB simply reuses it. Then, \advB uses the corresponding user and
  credential identifiers as parameters to a query to its own \SIGN oracle
  (specifying $\feval^{\attrs}$ as signature evaluation function). Eventually,
  $\adv$ outputs two user indexes, a ring $R$, and message \msg. If the checks
  at lines 3-4 of \figref{fig:model-rs} pass, \advB generates the challenge
  signature by calling its own \CHALb oracle, and passes the result to $\adv$.
  Finally, \advB outputs whatever $\adv$ outputs.
  %
  The simulation of \adv's anonymity game is perfect, and \advB wins its game
  whenever \adv~ does.
  \qed
\end{proof}

@@

\begin{proof}
  Assume $\adv$ against unforgeability of \CUASRing wins the game. We build
  \advB winning the non-frameability game of \CUASGen with the same probability.
  %
  \advB prepares the environment as the adversary \advB against anonymity, and
  answers \adv's queries to the \oracle{SIGN} oracle also as in the anonymity
  proof. To answer \adv's queries to its \oracle{CORR} oracle, \advB leverages
  the \ICORR oracle in the non-frameability game for \UAS. Finally, \advB
  outputs whatever $\adv$ outputs.

  Note that, if $\adv$ wins its game, it means that the public keys of the
  issuers in $R$ all belong to uncorrupted users. Since the signature is
  accepted by $Verify$ at line 3 of the ring signature unforgeability game,
  it is also accepted by \Verify in the \UAS non-frameability game. But,
  moreover, given the construction of $Verify$ in \CUASRing, there is some
  honest \usk within $R$ that produced the signature, so $\OWNR[\scid] \in \HU$
  in \advB's non-frameability game. Also, since $\adv$ never queried its
  \oracle{SIGN} oracle, then by construction there cannot exist a matching entry
  in \advB's $\SIG[\uid]$ table. Thus, \advB wins the non-frameability game
  whenever $\adv$ wins its unforgeability game. Since \CUASGen is non-frameable,
  then this probability must be negligible.
  %
  \qed
\end{proof}

@@

We prove that \CUASAC is an anonymous and unforgeable anonymous credential
scheme, according to \cite{fhs19}, if the underlying \CUASGen construction
is anonymous and unforgeable. Note that AC schemes modelled as in \cite{fhs19}
do not have issuance anonymity, as the user public key is passed to the issuer.
For ease of reference to the games in \secref{sec:formal-uas}, we
reduce to security of \CUASGen rather than to $\CUASGen^{int}$. The
``translation'' between \CUASGen and $\CUASGen^{int}$ is trivial, though.

\begin{theorem}[Anonymity of \CUASAC]
  \label{thm:anon-cuasac}
  If the base \CUASGen construction has signature anonymity according to
  \defref{def:sign-anonymity-uas}, then \CUASAC is an anonymous AC scheme
  according to \cite{fhs19}.
\end{theorem}

@@

  To simulate oracle calls by \adv, \advB simply redirects to its corresponding
  oracle, i.e.: for calls to \oracle{HU}, \oracle{CU}, \oracle{Obtain},
  \oracle{Show}, \oracle{LoR}, \advB redirects to
  \HUGEN, \CUGEN, \OBTAIN, \SIGN, \CHALb, respectively. Note that translating
  the inputs from the former into inputs for the latter is trivial.
  Obviously, if \adv~wins in its anonymity game, then so does \advB with the
  same probability.
  % 
  \qed
\end{proof}

### 2022-10-05 prism-backend/research/gsac/app-uas-proofs.tex
Typos and notation fixed. Some important updates pending...

Next, we define the \SimSetup, \ExtractIssue, \ExtractSign, and \VerCred
functions. \SimSetup (formally defined in \figref{fig:helper-funcs}) essentially
replaces the \Setup algorithm of each NIZK with the corresponding \NIZKSimSetup
algorithm, and returns the generated parameters along with the
trapdoors. \ExtractIssue and \ExtractSign simply run the \Extract functions
of the corresponding \NIZK scheme, leveraging the trapdoor produced during
\SimSetup. Note that, in our games definitions, both algorithms are always run
over signatures that have already been verified (in the case of \ExtractSign)
or transcripts maintained by honest issuers (in the case of \ExtractIssue).
Thus, the zero-knowledge proofs they contain are valid. Concerning \SimSetup,
due to the zero-knowledge and simulation extractability properties
(respectively) of the underlying NIZKs, its result is indistinguishable from
that of \Setup, and the extracted values match those used as witnesses in the
proofs. Finally, \VerCred simply calls the \SBCMVerify function with the
received data -- where \usk is signed in committed form, \cid and \attrs in
plain form, and \cred is their alleged signature by the owner of public key
\ipk.

\begin{figure}[ht!]
  \centering  
  \scalebox{0.9}{
    \begin{minipage}[t]{\textwidth}
      \procedure{$\SimSetup(1^\secpar)$}{%
        \textrm{Parse}~\secpar~\textrm{as}~(\Csecpar,\NIZKsecpar,\SBCMsecpar,
        \Esecpar). \\
        % \Cparm \gets \CSetup(\Csecpar), 
        \SBCMparm \gets  \SBCMSetup(\SBCMsecpar) \\
        % \Sparm \gets \SSetup(\Ssecpar), 
        \Eparm \gets \ESetup(\Esecpar) \\
        (\NIZKcrs_{\Issue},\trap_{\Issue}) \gets
        \NIZKSimSetup^{\NIZKRel_{\Issue}}(\NIZKsecpar) \\
        (\NIZKcrs_{\Sign},\trap_{\Sign}) \gets
        \NIZKSimSetup^{\NIZKRel_{\Sign}}(\NIZKsecpar) \\
        (\NIZKcrs_{\Open},\trap_{\Open}) \gets
        \NIZKSimSetup^{\NIZKRel_{\Open}}(\NIZKsecpar) \\
        \pcreturn ((% \Cparm,
        \SBCMparm,% \Sparm,
        \Eparm,\NIZKcrs_{\Issue},
        \NIZKcrs_{\Sign},\NIZKcrs_{\Open},\AttrSpace),
        (\trap_{\Issue},\trap_{\Sign},\trap_{\Open}))
      }

@@

  Game 1: We simulate the NIZK proof corresponding to $\NIZKRel_{\Issue}$ that
  the \OBTCHALb oracle produces when queried by \adv. The zero-knowledge
  property of the NIZK system ensures that game 1 is indistinguishable from
  the original experiment.

  Game 2: In queries to \OBTCHALb, before simulating the NIZK proof, we replace
  the produced \yissue value with a random element from \rngfissue. Since
  \fissue is a \UAS-acceptable function, game 2 is indistinguishable from game
  1.

  From an adversary \adv~against Game 2, we can build an adversary \advB against
  \SBCM's blindness property. The simulation that
  \advB does is straightforward. \advB runs Game 2 for \adv, randomly picking
  a number $q < n$, where $n$ is the number of users that \adv~creates via
  \HUGEN, and assigning to the $q$-th user the $(\SBCMvk,\SBCMsk)$ key pair
  that \advB receives in its blindness game. Then, when \adv~makes a query
  to its \OBTCHALb oracle, if the chosen issuer is the $q$-th user, \advB
  forwards \adv's messages to its own $\langle COM(\SBCMvk,
  \overline{\smsg}_{\bin},\smsg),\cdot\rangle$ oracle. Finally, \advB outputs
  whatever \adv~does. Note that, since in Game 2 we replace the \yissue value
  with a random value, and simulate the $\NIZKRel_{\Issue}$ proof, \adv~is not
  receiving information about the blindly signed messages beyond what \advB
  forwards from its own oracle. Thus, if \adv~wins in its game, \advB wins in
  its blindness game. However, since \advB has to guess the correct user
  that \adv~will use as issuer in its \OBTCHALb oracle, we have a $1/n$ security
  loss, where $n$ is the total number of users created by \adv.
  %
  \qed
\end{proof}

@@

  Observe that we restrict to credentials issued by honest issuers. Thus, if a
  credential with identifier \cid was issued by an honest issuer, a matching
  $\trans[\cid]$ entry corresponding to its issuance must exist.
  %
  Then, $\trans[\cid] = (\yissue,\utrans)$, and \utrans contains a NIZK proof
  \proofiss proving knowledge by the (potentially corrupt) user of a witness in
  \RelIss. Since the issuer is honest, it verifies the NIZK as part of the
  issuance protocol, rejecting if the proof is not valid. Thus, by simulation
  extractability, \ExtractIssue produces a $(\upk,\usk,\lbrace (\cid_i,\attrs_i,
  \cred_i,\ipk_i) \rbrace_{i\in[n]},(\cid,\attrs,\cred,\ipk))$ tuple.

@@

  Finally, the adversary may also win if any of the $\cred_i$ credentials (1) is
  not a valid signature by its issuer, or (2) if it is a valid signature by some
  honest issuer who did not produce it. As before, (1) has negligible
  probability due to simulation extractability of the NIZK for \RelIss. For (2),
  assume that such a $\cred_i$ exists, then, it is an \SBCM forgery -- i.e., a
  valid signature, verifiable under $\ipk_i$ belonging to an honest issuer, who
  did not produce it via a call to \OBTISS or \ISSUE. Thus, it breaks the
  one-more unforgeability property of \SBCM. By security of \SBCM, the
  probability that it happens must be negligible.
\end{proof}

@@

  \paragraph{(a) \Judge accepts $(\yinsp,\iproof)$.} %
  Simulation extractability of $\NIZK^{\Sign}$ ensures that $\cinsp =
  \EEnc(\Eek,\yinsp)$, and since $(\yinsp,\iproof)$ is generated honestly at
  line 5, then \yinsp is the correct decryption of \cinsp, and completeness of
  $\NIZK^{\Open}$ ensures that \Judge outputs $1$ at line 6.

  \paragraph{(b) $(\yeval^0,\yeval^1)$ are the correct signature evaluation
    pair.} Also, due to simulation extractability of $\NIZK^{\Sign}$:

@@

  Thus, the probability of \adv~winning at line 12 is negligible, due to
  simulation extractability of $\NIZK^{\Sign}$.

  \paragraph{(c) The output of \finsp matches the output of \Open.} %
  After (a), and correctness of the public key encryption algorithm, the \yinsp
  value output by \Open is the correct decryption of
  \cinsp. After (c), the $(\yeval^0=\yeval,\yeval^1)$ values output by
  \ExtractSign match the evaluation of \feval. Thus, simulation extractability
  of $\NIZK^{\Sign}$ ensures that $\finsp((\yeval^0,\yeval^1),\upk,\lbrace
  (\cid_i,\attrs_i)\rbrace_{i\in[n]},\msg) = \yinsp$ and, also, that \yinsp
  matches the $\yinsp'$ value extracted by \ExtractSign. Thus, the probability
  of \adv~winning at line 13 is negligible due to simulation extractability
  of $\NIZK^{\Sign}$.

  \paragraph{(d) All {\cred}s are bound to the \usk of a known \uid.} %
  $\NIZKRel^{\Sign}$ includes a condition that $\forall i\in[n],
  \SBCMVerify(\ipk_i,\cred_i,\usk,\attrs_i) = 1$. Thus, simulation
  extractability of $\NIZK^{\Sign}$ and correctness of \SBCM, ensure that all
  credentials involved in the signature contain the same \usk as their user key
  (first) attribute. Thus, either $\OWNR[\lbrace \cid_i \rbrace_{i\in[n]}]$
  returns some \uid in $\HU \cup \CU$, or it returns $\bot$ because no such
  \uid exists (but not because more than one \cid belongs to different {\uid}s).
  Assume that no such \uid exists. Then, the {$\cred_i$}s extracted by
  \ExtractSign cannot have been produced via a call to either \OBTISS or \ISSUE,
  since they only accept calls from known {\uid}s (either in \HU or \CU,
  respectively). Since, by simulation extractability of $\NIZK^{\Sign}$, at
  least one such credential must have been used to produce the signature, then
  this breaks the one-more forgery property of the underlying \SBCM.
  %
  \qed
\end{proof}

@@

  Since the signature output by \adv~is accepted by \Verify at line 4,
  simulation extractability of $\NIZK^{\Sign}$ ensures that $\yeval = \yeval^0$,
  and $\tyeval^1 = \yeval^1$. Similarly, if the $(\yinsp,\iproof)$
  pair output by \adv~is accepted by \Judge, simulation extractability of
  $\NIZK^{\Sign}$ and $\NIZK^{\Open}$ implies that both checks at lines 8 and 9
  pass. Hence, the probability that the adversary wins at either lines 8 or 9 is
  negligible, after simulation extractability of $\NIZK^{\Sign}$ and
  $\NIZK^{\Open}$.

  Next, we prove that, after zero-knowledge and simulation extractability of
  $\NIZKRel_{\Sign}$, and blindness of \SBCM, no credential from an honest user
  can be extracted from the signature output by \adv, except with negligible
  probability.
  %
  The crucial observation is that, as in \cite{cl06} \CUASGen's \Sign algorithm
  produces a signature of knowledge for the relation defined by
  $\NIZKRel^{\Sign}$. That is, given $(x,w) \in \NIZKRel^{\Sign}$, one can
  compare $x$ and $w$ to the public and private key of a signature algorithm,
  respectively. In $\NIZKRel^{\Sign}$, $(\upk,\usk,\lbrace (\cid_i,\attrs_i,
  \cred_i)\rbrace_{i\in[n]},\yeval^1,\yinsp,r,r')$ is the private key ($w$), and
  $(\msg,\feval,\yeval^0,\cinsp,\lbrace \ipk_i \rbrace_{i\in[n]},\Eek)$ is the
  public key ($x$).
  %
  From this, we prove that an adversary has only negligible probability to forge
  a signature as originating from an honest user without calling the \SIGN
  oracle. The strategy is similar to that in \cite[Theorem 2.1]{cl06}.

  Consider game $G_1$, which is equivalent to $G_0 = \ExpNonframe$, except that
  in the \Sign function within the \SIGN oracle, we simulate the NIZK proof.
  After the zero-knowledge property of $\NIZK^{\NIZKRel_{\Sign}}$, $G_1$ is
  indistinguishable from $G_0$. Now, in $G_1$, simulation extractability of
  $\NIZK^{\NIZKRel_{\Sign}}$ ensures that \ExtractSign outputs a valid
  witness for $(\msg,\feval,\yeval^0,\cinsp,\lbrace ipk_i \rbrace_{i\in[n]},
  \Eek)$. Note that this witness must include some \usk which, in case of
  being owned by an honest user, has not been leaked to \adv~--as the user
  has not been corrupted, nor the \usk has been leaked via \SIGN queries,
  where the proof of knowledge within \Sign is now simulated). Moreover,
  blindness of \SBCM ensures that the issuer (who is potentially corrupt), did
  not learn \usk either during calls to \OBTAIN. Thus, since \usk is picked
  uniformly at random by honest users, the probability that $\UK[\uid] = \usk$
  for $\uid \in \HU$ and \Sig produced by the adversary, is negligible.
  %
  \qed
\end{proof}

>>>>

Next, we define the \SimSetup, \ExtractIssue, \ExtractSign, and \VerCred
functions. \SimSetup (formally defined in \figref{fig:helper-funcs}) essentially
replaces the \Setup algorithm of each NIZK with the corresponding \NIZKSimSetup
algorithm, and returns the generated parameters along with the trapdoors.
\ExtractIssue and \ExtractSign simply run the \helper{\Extract} functions of the
corresponding \NIZK scheme, leveraging the trapdoor produced during \SimSetup.
Note that, in our games definitions, both algorithms are always run over
signatures that have already been verified (in the case of \ExtractSign)
or transcripts maintained by honest issuers (in the case of \ExtractIssue).
Thus, the zero-knowledge proofs they contain are valid. Concerning \SimSetup,
due to the zero-knowledge and simulation extractability properties
(respectively) of the underlying NIZKs, its result is indistinguishable from
that of \Setup, and the extracted values match those used as witnesses in the
proofs. Finally, \VerCred simply calls the \SBCMVerify function with the
received data -- where \usk is signed in committed form, \cid and \attrs in
plain form, and \cred is their alleged signature by the owner of public key
\ipk.

\begin{figure}[ht!]
  \centering  
  \scalebox{0.9}{
    \begin{minipage}[t]{\textwidth}
      \procedure{$\SimSetup(1^\secpar)$}{%
        % \Cparm \gets \CSetup(\Csecpar), 
        \SBCMparm \gets  \SBCMSetup(\secpar) \\
        % \Sparm \gets \SSetup(\Ssecpar), 
        \Eparm \gets \ESetup(\secpar) \\
        (\NIZKcrs_{\Issue},\trap_{\Issue}) \gets
        \NIZKSimSetup^{\RelIss}(\secpar) \\
        (\NIZKcrs_{\Sign},\trap_{\Sign}) \gets
        \NIZKSimSetup^{\RelSig}(\secpar) \\
        (\NIZKcrs_{\Open},\trap_{\Open}) \gets
        \NIZKSimSetup^{\RelIns}(\secpar) \\
        \pcreturn ((% \Cparm,
        \SBCMparm,% \Sparm,
        \Eparm,\NIZKcrs_{\Issue},
        \NIZKcrs_{\Sign},\NIZKcrs_{\Open},\AttrSpace),
        (\trap_{\Issue},\trap_{\Sign},\trap_{\Open}))
      }

@@

  Game 1: We simulate the NIZK proof corresponding to \RelIss that
  the \OBTCHALb oracle produces when queried by \adv. The zero-knowledge
  property of the NIZK system ensures that game 1 is indistinguishable from
  the original experiment.

  Game 2: In queries to \OBTCHALb, before simulating the NIZK proof, we replace
  the produced \yissue value with a random element from $\rngfissue \setminus
  0$. Since \fissue is a \UAS-acceptable function, game 2 is indistinguishable
  from game 1.

  From an adversary \adv~against Game 2, we can build an adversary \advB against
  \SBCM's blindness property. The simulation that
  \advB does is straightforward. \advB runs Game 2 for \adv, randomly picking
  a number $q < n$, where $n$ is the number of users that \adv~creates via
  \HUGEN, and assigning to the $q$-th user the \vk key that \advB receives in
  its blindness game. Then, when \adv~makes a query to its \OBTCHALb oracle, if
  the chosen issuer is the $q$-th user, \advB forwards \adv's messages to its
  own \oracle{BLIND} oracle. Finally, \advB outputs \todo{XXXX UPDATE}
  whatever \adv~does. Note that, since in Game 2 we replace the \yissue value
  with a random value, and simulate the \RelIss proof, \adv~is not
  receiving information about the blindly signed messages beyond what \advB
  forwards from its own oracle. Thus, if \adv~wins in its game, \advB wins in
  its blindness game. However, since \advB has to guess the correct user
  that \adv~will use as issuer in its \OBTCHALb oracle, we have a $1/n$ security
  loss, where $n$ is the total number of users created by \adv.
  %
  \qed
\end{proof}

@@

  Observe that we restrict to credentials issued by honest issuers. Thus, if a
  credential with identifier \cid was issued by an honest issuer, a matching
  $\trans[\cid]$ entry corresponding to its issuance must exist.
  %
  Then, $\trans[\cid] = (\yissue,\utrans)$, and \utrans contains a NIZK proof
  \NIZKproof proving knowledge by the (potentially corrupt) user of a witness in
  \RelIss. Since the issuer is honest, it verifies the NIZK as part of the
  issuance protocol, rejecting if the proof is not valid. Thus, by simulation
  extractability, \ExtractIssue produces a $(\upk,\usk,\lbrace (\cid_i,\attrs_i,
  \cred_i,\ipk_i) \rbrace_{i\in[n]},(\cid,\attrs,\cred,\ipk))$ tuple.

@@

  Finally, the adversary may also win if any of the $\cred_i$ credentials (1) is
  not a valid signature by its issuer, or (2) if it is a valid signature by some
  honest issuer who did not produce it. As before, (1) has negligible
  probability due to simulation extractability of the NIZK for \RelIss. For (2),
  assume that such a $\cred_i$ exists, then, it is an \SBCM forgery -- i.e., a
  valid signature, verifiable under $\ipk_i$ belonging to an honest issuer, who
  did not produce it via a call to \OBTISS or \ISSUE. Thus, it breaks the
  one-more unforgeability property of \SBCM. By security of \SBCM, the
  probability that it happens must be negligible.
  %
  \qed
\end{proof}

@@

  \paragraph{(a) \Judge accepts $(\yinsp,\iproof)$.} %
  Simulation extractability of the NIZK for \RelSig ensures that $\cinsp =
  \EEnc(\Eek,\yinsp)$, and since $(\yinsp,\iproof)$ is generated honestly at
  line 5, then \yinsp is the correct decryption of \cinsp, and completeness of
  the NIZK for \RelIns ensures that \Judge outputs $1$ at line 6.

  \paragraph{(b) $(\yeval^0,\yeval^1)$ are the correct signature evaluation
    pair.} Also, due to simulation extractability of the NIZK for \RelSig:

@@

  Thus, the probability of \adv~winning at line 12 is negligible, due to
  simulation extractability of the NIZK for \RelSig.

  \paragraph{(c) The output of \finsp matches the output of \Open.} %
  After (a), and correctness of the public key encryption algorithm, the \yinsp
  value output by \Open is the correct decryption of
  \cinsp. After (c), the $(\yeval^0=\yeval,\yeval^1)$ values output by
  \ExtractSign match the evaluation of \feval. Thus, simulation extractability
  of the NIZK for \RelSig ensures that $\finsp((\yeval^0,\yeval^1),\upk,\lbrace
  (\cid_i,\attrs_i)\rbrace_{i\in[n]},\msg) = \yinsp$ and, also, that \yinsp
  matches the $\yinsp'$ value extracted by \ExtractSign. Thus, the probability
  of \adv~winning at line 13 is negligible due to simulation extractability
  of the NIZK for \RelSig.

  \paragraph{(d) All {\cred}s are bound to the \usk of a known \uid.} %
  \RelSig includes a condition that $\forall i\in[n], 
  \SBCMVerify(\ipk_i,\cred_i,\usk,\attrs_i) = 1$. Thus, simulation
  extractability of the NIZK for \RelSig and correctness of \SBCM, ensure that
  all credentials involved in the signature contain the same \usk as their user
  key  (first) attribute. Thus, either $\OWNR[\lbrace \cid_i \rbrace_{i\in[n]}]$
  returns some \uid in $\HU \cup \CU$, or it returns $\bot$ because no such
  \uid exists (but not because more than one \cid belongs to different {\uid}s).
  Assume that no such \uid exists. Then, the {$\cred_i$}s extracted by
  \ExtractSign cannot have been produced via a call to either \OBTISS or \ISSUE,
  since they only accept calls from known {\uid}s (either in \HU or \CU,
  respectively). Since, by simulation extractability of the NIZK for \RelSig at
  least one such credential must have been used to produce the signature, then
  this breaks the one-more forgery property of the underlying \SBCM.
  %
  \qed
\end{proof}

@@

  Since the signature output by \adv~is accepted by \Verify at line 4,
  simulation extractability of the NIZK for \RelSig ensures that $\yeval =
  \yeval^0$, and $\tyeval^1 = \yeval^1$. Similarly, if the $(\yinsp,\iproof)$
  pair output by \adv~is accepted by \Judge, simulation extractability of
  the NIZKs for \RelSig and \RelIns implies that both checks at lines 8 and 9
  pass. Hence, the probability that the adversary wins at either lines 8 or 9 is
  negligible, after simulation extractability of the NIZKs for \RelSig and
  \RelIns.

  Next, we prove that, after zero-knowledge and simulation extractability of the
  NIZK for \RelSig, and blindness of \SBCM, no credential from an honest user
  can be extracted from the signature output by \adv, except with negligible
  probability.
  %
  The crucial observation is that, as in \cite{cl06} \CUASGen's \Sign algorithm
  produces a signature of knowledge for the relation defined by \RelSig
  That is, given $(x,w) \in \NIZKRel^{\Sign}$, one can compare $x$ and $w$ to
  the public and private key of a signature algorithm, respectively. In \RelSig,
  $(\upk,\usk,\lbrace (\cid_i,\attrs_i,
  \cred_i)\rbrace_{i\in[n]},\yeval^1,\yinsp,r,r')$ is the private key ($w$), and
  $(\msg,\feval,\yeval^0,\cinsp,\lbrace \ipk_i \rbrace_{i\in[n]},\ek)$ is the
  public key ($x$).
  %
  From this, we prove that an adversary has only negligible probability to forge
  a signature as originating from an honest user without calling the \SIGN
  oracle. The strategy is similar to that in \cite[Theorem 2.1]{cl06}.

  Consider game $G_1$, which is equivalent to $G_0 = \ExpNonframe$, except that
  in the \Sign function within the \SIGN oracle, we simulate the NIZK proof.
  After the zero-knowledge property of the NIZK for \RelSig, $G_1$ is
  indistinguishable from $G_0$. Now, in $G_1$, simulation extractability of
  the NIZK for \RelSig ensures that \ExtractSign outputs a valid
  witness for $(\msg,\feval,\yeval^0,\cinsp,\lbrace ipk_i \rbrace_{i\in[n]},
  \ek)$. Note that this witness must include some \usk which, in case of
  being owned by an honest user, has not been leaked to \adv~--as the user
  has not been corrupted, nor the \usk has been leaked via \SIGN queries,
  where the proof of knowledge within \Sign is now simulated). Moreover,
  blindness of \SBCM ensures that the issuer (who is potentially corrupt), did
  not learn \usk either during calls to \OBTAIN. Thus, since \usk is picked
  uniformly at random by honest users, the probability that $\UK[\uid] = \usk$
  for $\uid \in \HU$ and \Sig produced by the adversary, is negligible.
  %
  \qed
\end{proof}
